The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
mv hr size down
add kasozi 2020

## Caribou location data
We used GPS location data collected from `r DT[, uniqueN(get(idcol))]` adult female caribou on Fogo Island, Newfoundland, Canada between 
`r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`. 
Caribou were immobilized and fitted with global positioning
system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
collars, 1,250 g) as described by Schaefer and Mahoney [-@Schaefer_2013]. Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
to remove all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
proportion of marked adult females was ~10% of all adult females and ~5% of all
individuals in the herd. We assumed these individuals were randomly distributed
throughout the population.

## Landscape data and habitat classification
Land cover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification
included nine habitat types at 30 m resolution. We reclassified the land cover
types into three categories using the R package `raster` [@Hijmans_2019]:
foraging, forest, and open habitats. Foraging habitat consisted of lichen,
forest habitat consisted of coniferous forest, conifer scrub, broad leaf forest,
and mixed-wood forest, while open habitat consisted of wetland, rocky barrens,
and anthropogenic areas. Water was excluded from all subsequent analyses.

@@

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. The chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment is defined using a 
temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. 
In all networks, individual caribou were represented as nodes and associations between
individuals were represented as edges. We weighted edges by the strength of 
association between individuals using the simple ratio index [SRI, @Cairns_1987].

>>>>

## Caribou location data
We used GPS location data collected from `r DT[, uniqueN(get(idcol))]` adult female caribou on Fogo Island, Newfoundland, Canada between 
`r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`. 
Caribou were immobilized and fitted with global positioning
system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
collars, 1,250 g) as described by Schaefer and Mahoney [-@Schaefer_2013]. Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
to remove all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
proportion of marked adult females was ~10% of all adult females and ~5% of all
individuals in the herd. We assumed these individuals were randomly distributed
throughout the population. Home range sizes for 
caribou on Fogo Island are on average 50.1 $km^2$ in winter and 17.5 $km^2$ in 
summer [@Peignier_2019].

## Landscape data and habitat classification
Land cover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]. Available land cover classification
included nine habitat types at 30 m resolution. We reclassified the land cover
types into three categories using the R package `raster` [@Hijmans_2019]:
foraging, forest, and open habitats. Foraging habitat consisted of lichen,
forest habitat consisted of coniferous forest, conifer scrub, broad leaf forest,
and mixed-wood forest, while open habitat consisted of wetland, rocky barrens,
and anthropogenic areas. Water was excluded from all subsequent analyses.

@@

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008; @Kasozi_2020]. 
The chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment is defined using a 
temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. 
In all networks, individual caribou were represented as nodes and associations between
individuals were represented as edges. We weighted edges by the strength of 
association between individuals using the simple ratio index [SRI, @Cairns_1987].
